DATA 621 - Business Analytics and Data Mining

### 2020-09-24 HW2/HW2-Group2.rmd
Copyedit and expand section 10 prose

10. ROC Curve
The ROC curve is defined as a plot of the true positive rate against the false
positive rate at different probability thresholds. The false positive rate is
usually plotted on the x-axis.

```{r ROC}
ROC <- function(df) {
  if (!is.data.frame(df)) {
    stop("Data set is not a dataframe. Try as.data.frame(dataset).")
  } else {
    rocTable <- data.table(thresh = seq(0, 1, 0.01),
                           x = double(101),
                           y = double(101))
    for (i in seq_along(rocTable$thresh)) {
      dftmp <- data.frame(class = df$class,
                          pred_class = ifelse(df$pred_prob > rocTable$thresh[i],
                                              1, 0))
      rocTable$x[i] <- 1 - SPC(dftmp)
      rocTable$y[i] <- SNS(dftmp)
    }
    plot(rocTable$x, rocTable$y, type = 'l')
  }
}
```

>>>>

10. ROC Curve
The receiver operating curve (ROC) is defined as a plot of the true positive
rate (TPR) against the false positive rate (FPR) at different probability
thresholds. The FPR is usually plotted on the x-axis. The function below takes
as input a data frame with columns named `class` and `pred_class` as above, and
a third column named `pred_prob` which reflects the predicted probability of
being positive. It then steps along a sequence from 0 to 1, assigning classes
based on that sequence, calculating the TPR and FPR for each threshold, plotting
the results when completed. Lastly, it calculates the area under the ROC (AUC).

```{r ROC}
ROC <- function(df) {
  if (!is.data.frame(df)) {
    stop("Data set is not a dataframe. Try as.data.frame(dataset).")
  } else {
    rocTable <- data.table(thresh = seq(0, 1, 0.01),
                           x = double(101),
                           y = double(101))
    for (i in seq_along(rocTable$thresh)) {
      dftmp <- data.frame(class = df$class,
                          pred_class = ifelse(df$pred_prob > rocTable$thresh[i],
                                              1, 0))
      rocTable$x[i] <- 1 - SPC(dftmp)
      rocTable$y[i] <- SNS(dftmp)
    }
    plot(rocTable$x, rocTable$y, type = 'l', xlab = "False Positive Rate",
         ylab = 'True Positive Rate')
  }
}
```
